

---
title: "Dataset Usage"
author: "John Waller"
date: "May 4, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, echo=FALSE, warning=FALSE, message=FALSE}
# get downloaded datasets 
Files = list.files("C:/Users/ftw712/Desktop/usageReport/data/datasets/") # load datasets
# Files = Files[Files %in% list.files("C:/Users/ftw712/Desktop/usageReport/data/filter_data/filterData/")]

File = Files[11]
# File = "18c93d12-34fb-4d3f-903c-b77215a1dcc9.rda"
# load data 
source("C:/Users/ftw712/Desktop/usageReport/R/loadData.r")
loadData(File)
```

## `r Title`
## https://www.gbif.org/dataset/`r Key`

## How many downloads through time?  

Here I plot the total downloads and then group by month to make the plot smoother. 

```{r,echo=FALSE, warning=FALSE, message=FALSE,}
# When were most downloads happening? 
source("C:/Users/ftw712/Desktop/usageReport/R/whenSearchesHappened.r")
whenSearchHappened(dataset)
```

## Top 10 Taxon Searches

What taxon_key was used during the occurrence download? 

Here I grouped by rank. This graph was in fact **very expensive** to compute because I had to look up the rank for each taxon key before it could be grouped. Might be best used only in **annual reporting** even though it is informative. 

```{r, echo=FALSE, warning=FALSE, message=FALSE}
source("C:/Users/ftw712/Desktop/usageReport/R/taxonSearchCountsPlot.r")
taxonSearchCountPlots(top10,File,Title)
```

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# rankChoices = c("SPECIES","GENUS","FAMILY","ORDER","CLASS","KINGDOM")
source("C:/Users/ftw712/Desktop/usageReport/R/getImageLinks.r")
linksGenus = getImageLinks(top10,"GENUS")
linksSpecies = getImageLinks(top10,"SPECIES")
```

## Images

Images for the top 10 searched taxon keys for species and genus. 

### Top 10 Images for species 
```{r,out.width='10%', echo=FALSE}
knitr::include_graphics(linksSpecies)
```

### Top 10 Images for genus 
```{r,out.width='10%', echo=FALSE}
knitr::include_graphics(linksGenus)
```

## Top search filter used when dataset was hit

This graph is almost always **very similar between datasets**. See: http://rpubs.com/JohnWaller/387693

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.height=7,fig.width=7}
source("C:/Users/ftw712/Desktop/usageReport/R/plotFilters.r")
plotFilters(filterData)
```


## Top searched country for dataset 
This is the **country that was searched** not the country that the search was coming from. 

```{r, echo=FALSE, warning=FALSE, message=FALSE}
source("C:/Users/ftw712/Desktop/usageReport/R/countryPlot.r")
topSearchedCountries(filterData)
```







